GEE models

### 2017-10-15 doc/manuscript.Rmd
added another ref to DAG

Covariate selection was based on previous literature, directed acyclic graph 
[@Greenland1999a;@Textor2011a] recommendations (see `r cite_sf("dag_isi")` and 
`r cite_sf("dag_issi2")`), and quasi-likelihood information criterion (QIC) [@Pan2001a]. See
the ESM Methods for more detail on QIC and the directed acyclic graphs. 
`r cite_st('qic')` shows the covariates compared using QIC. We selected the
model (M9) that had the fewest covariates and that had similar fit between the
outcome measures. The final GEE model included the covariates years from baseline
(time), sex (female or male), ethnicity (European ancestry or non-European 
ancestry), baseline age, WC, ALT, and MET (physical activity). Sex, ethnicity, 
and baseline age were time-*independent* variables. See the ESM Methods for more
detail on the covariate inclusion. After scaling,
and log-transforming the model variables, then exponentiating the GEE estimates,
the interpretation of the GEE results is as an expected percent difference in 
the outcome variable for every standard deviation (SD) increase in the predictor
variable, for the same covariate values (e.g. same age or sex). With the main effect 
associations (not with a time interaction), this interpretation is applied 
consistently at each time point and thus represents associations of baseline 
NEFA for each future value of the outcomes. Since TAG is a risk factor for
diabetes and since NEFA contribute to TAG production [@Barrows2006a], TAG may
act as a mediator between NEFA and the outcomes. To determine the role of TAG in
the association between NEFA and the outcomes, TAG was included in the GEE model
in a sensitivity analysis. Lastly for the GEE models, we tested for an 
interaction with sex, ethnicity, or time by the predictor term for each outcome 
variable.

>>>>

Covariate selection was based on previous literature, directed acyclic graph 
[@Greenland1999a;@Textor2011a;@Shrier2008a] recommendations (see `r cite_sf("dag_isi")` and 
`r cite_sf("dag_issi2")`), and quasi-likelihood information criterion (QIC) [@Pan2001a]. See
the ESM Methods for more detail on QIC and the directed acyclic graphs. 
`r cite_st('qic')` shows the covariates compared using QIC. We selected the
model (M9) that had the fewest covariates and that had similar fit between the
outcome measures. The final GEE model included the covariates years from baseline
(time), sex (female or male), ethnicity (European ancestry or non-European 
ancestry), baseline age, WC, ALT, and MET (physical activity). Sex, ethnicity, 
and baseline age were time-*independent* variables. See the ESM Methods for more
detail on the covariate inclusion. After scaling,
and log-transforming the model variables, then exponentiating the GEE estimates,
the interpretation of the GEE results is as an expected percent difference in 
the outcome variable for every standard deviation (SD) increase in the predictor
variable, for the same covariate values (e.g. same age or sex). With the main effect 
associations (not with a time interaction), this interpretation is applied 
consistently at each time point and thus represents associations of baseline 
NEFA for each future value of the outcomes. Since TAG is a risk factor for
diabetes and since NEFA contribute to TAG production [@Barrows2006a], TAG may
act as a mediator between NEFA and the outcomes. To determine the role of TAG in
the association between NEFA and the outcomes, TAG was included in the GEE model
in a sensitivity analysis. Lastly for the GEE models, we tested for an 
interaction with sex, ethnicity, or time by the predictor term for each outcome 
variable.
